---
title: "Course9week4 Assignment-Cherry"
author: "Cherry"
date: "9/23/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Assignment Introduction

It is required to create a Shiny application and deploy it on Rstudio's servers. 

The application must include the following:

1. Some form of input (widget: textbox, radio button, checkbox, ...)
2. Some operation on the ui input in sever.R
3. Some reactive output displayed as a result of server calculations
4. You must also include enough documentation so that a novice user could use your application.
5. The documentation should be at the Shiny website itself. Do not post to an external link.

## Brief introduction of my shiny app1

I plan to use datasets "cars" as the supporting materials. It gives the speed of cars and the distances taken to stop. 

```{r cars, echo = TRUE}
plot(cars)
```

## Brief introduction of my shiny app2

Based on the simple analysis, we can tell the stopping distances has a linear correlation with car speed. 

```{r, echo=FALSE}
plot(cars)
pred <- lm(dist~speed, data = cars)
abline(pred, col="red")
```

## Brief introduction of my shiny app3

So I create a shiny app to predict the stopping distance by entering a car speed.

You can find my shiny app at : <https://cherrychen.shinyapps.io/cherry-developing_data_products/>

The ui.R and server.R code can be found at : <https://github.com/spoiledcherry/course9week4.git>

Thank you!
